Tropical Mathematics for the Lambda Calculus

### 2023-01-16 section3C.tex
Ho rimesso il differenziale nella sua forma originale

\begin{definition}
 Let $\widetilde{(\cdot)}:\HOM{\LREL}{!X}{Y}\to \HOM{\LREL}{!(X+X)}{Y}$, $\widetilde t_{\mu\oplus\rho,b}:= t_{\mu*\rho,b}$, and $d:\HOM{\LREL}{!(X+X)}{Y}\to \HOM{\LREL}{!(X+X)}{Y}$, $(dt)_{\mu\oplus\rho,b}:=t_{\rho\oplus\mu,b}$ if $\#\mu_1=1$ and $(dt)_{\mu\oplus\rho,b}:=\infty$ otherwise.
 The \emph{tropical differential operator} is the map $D:=d\circ\widetilde{(\cdot)}:\HOM{\LREL}{!X}{Y}\to \HOM{\LREL}{!(X+X)}{Y}$.
\end{definition}

\begin{example}
For $t\in\HOM{\LREL}{!X}{Y}$, we have:
 $(Dt)_{\mu\oplus\rho,b}=t_{\rho*\mu,b}$ if $\#\mu_1=1$ and it is $\infty$ otherwise.
 Analogously, we have:
 $D^2 t\in\HOM{\LREL_!}{(X+X)+(X+X)}{Y}$, where $(D^2 t)_{(\rho\oplus\rho')\oplus(\nu\oplus\nu'),b}$ equals $t_{\nu*\nu'*\rho',b}$ if $\rho=\emptyset$ and $\#\rho'=1=\#\nu$; it equals $t_{\rho*\nu',b}$ if $\rho'=\emptyset=\nu$ and $\#\rho=1$; it equals $\infty$ otherwise.
\end{example}

>>>>

\begin{definition}
 The \emph{tropical differential operator} is the map $D:\HOM{\LREL}{!X}{Y}\to \HOM{\LREL}{!(X+X)}{Y}$ defined as $(Dt)_{\mu\oplus\rho,b}=t_{\rho*\mu,b}$ if $\#\mu=1$ and as $\infty$ otherwise.
\end{definition}

\begin{remark}
For $t\in\HOM{\LREL}{!X}{Y}$, we have:
 $D^2 t\in\HOM{\LREL_!}{(X+X)+(X+X)}{Y}$, where $(D^2 t)_{(\rho\oplus\rho')\oplus(\nu\oplus\nu'),b}$ equals $t_{\nu*\nu'*\rho',b}$ if $\rho=\emptyset$ and $\#\rho'=1=\#\nu$; it equals $t_{\rho*\nu',b}$ if $\rho'=\emptyset=\nu$ and $\#\rho=1$; it equals $\infty$ otherwise.
\end{remark}
